Empty Homes V1

### 2017-05-25 EmptyHomesV1.Rmd
Includion of Southwark
Southwarks new data was included,. I attempted to include croydon but realsied I only have exemptions fromthem I will have to ask for discounts tomorrow. Hopefully it will be quicker than before.

test <- ls(pattern = "info") %>% map_df(~eval(parse(text=.x)))

>>>>

#City of London

CoLinfo <- read_excel("City of LondonExemptionsLSOAApril2017.xlsx" )[,1:4] %>%
  StructureData(c(2,3,4,13))

Southwarkinfo <- read_excel("Southwark discounts.xlsx")[1:4] %>%
  StructureData(empty = -c(1,2,5))

#Croydon
CroydonInfo

#All London With missing Boroughs
PlotMap(Southwarkinfo, AG)

 ls(pattern = "info") %>% map_df(~eval(parse(text=.x))) %>%
  PlotMap(., filter(AG, RGN15NM=="London"), filtermap = FALSE)

list.files()
```
